### 2018-07-10 paper/message-passing-design.tex
WIP editing of algorithms

\NewScheme{\POR}{POR}

\subsection{Message Passing through Predictive Onion Routes (PORs)}
\label{sec:message_passing}

@@

We have the Stateless Predictive Onion Routing scheme, \POR, which provides 
probabilistically onion-routed message passing.
Instead of providing only one address per hop in the route (as in \eg 
Tor~\cite{Tor}), \(\POR\) provides several alternatives for the next hop 
depending on their probability of being online.
To do this, \(\POR\) provides stateless algorithms for the onion-routing.

\(\POR\) provides three algorithms: \(\POR[\Send]\) (\cref{SPORSend}), 
\(\POR[\Fwd]\) (\cref{SPORFwd}) and \(\POR[\Recv]\) (\cref{SPORRecv}).
Say Alice wants to send a message \(m\) to Bob.
Bob uses \(\POR[\Recv]\) to create a probabilistic onion route \(H_\rdv\) from 
a rendez-vous point to his own device swarm --- all the hops on the route are 
chosen by Bob uniformly at random.
Bob gives \(H_\rdv\) to Alice using an out-of-band channel, \eg using his phone.
Alice uses \(\POR[\Send]\) at some later time to send the message to Bob using 
any of her devices.
\(\POR[\Send]\) extends the route \(H_\rdv\) with some hops of Alice's choosing 
(uniformly randomly chosen), then starts to forward the message (using 
\(\POR[\Fwd]\)) through the hops on the route to Bob.
This process is illustrated in \cref{fig:file-exchange}.

\begin{figure}
  \includegraphics[width=\linewidth]{figures/file_exchange_v2.pdf}
  \caption{\label{fig:file-exchange}%
    A schematic of Alice and Bob sending a message using \(\POR\).
  }
\end{figure}

\NewAlgorithm{\ExtendRoute}{ExtendRoute}
\NewAlgorithm{\CreateOnionLayer}{CreateOnionLayer}

\begin{figure}

  \framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}[1]
    \Require{%
      $H$ is a header of the form \(D\concat H'\) or \(D\concat \top\), where 
      \(D\) is a set of device addresses.
      $\pk_D$ is the public key of device set $D$.
      $L$ is the length of the route,
      $\theta$ is the threshold of probability of failure.%
    }
    \Function{\ExtendRoute}{$H, L, \theta$}
      \If{$L\leq 0$}
        \State \Return $H$
      \EndIf
      \State $D\gets \CreateOnionLayer[\theta]$
      \State $H\gets D\concat \DeBEenc[\mpk, D, H]$
      \State \Return $\ExtendRoute[H, L-1, \theta]$
    \EndFunction

    \Function{\CreateOnionLayer}{$\theta$}
      \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
      \State $D\gets \{(d, \pk_d, p_d)\}$
      \While{$\prod_{d\in D} p_d > \theta$}
        \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
        \State $D\gets D\cup \{(d, \pk_d, p_d)\}$
      \EndWhile
      \State \Return $D$
    \EndFunction
  \end{algorithmic}
  \end{minipage}}
  \caption{\label{ExtendRoute}%
    The \(\ExtendRoute\) algorithm extends a route \(H\) with \(L\) hops and 
    failure threshold of \(\theta\) for each hop in the route.
    Thus the probability of failure for the extension is \(1 - (1 - \theta)^L\).
    The function \(\GetRandomPeer\) is any random peer-sampling algorithm.
  }
\end{figure}

@@

>>>>

\NewScheme{\SPOR}

\subsection{\Acfp*{SPOR}}%
\label{sec:message_passing}

@@

We now describe a protocol \ac{SPOR}, which uses the \ac{POR} of Sphinxes to 
transfer large messages from a source to a destination.
We provide the following algorithms:
\begin{itemize}
  \item \(\SPOR[\Send]\) (\cref{SPORSend}).
  \item \(\SPOR[\Fwd]\) (\cref{SPORFwd}).
  \item \(\SPOR[\Recv]\) (\cref{SPORRecv}).
\end{itemize}

Say that Alice wants to send a message \(m\) to Bob.
Bob runs the \(\SPOR[\Recv]\) algorithm and Alice runs the \(\SPOR[\Send]\) 
algorithm.
Bob (\ie \(\SPOR[\Recv]\)) creates a reply header using \(\CreateRe\) and gives 
the output to Alice (\ie \(\SPOR[\Send]\)) out-of-band.
At a later point, Alice creates a forward header using \(\CreateFwd\), attaches 
the message \(m\) as payload and sends the package to the first node, \ie 
invokes the \(\SPOR[\Fwd]\) algorithm on the first node (\eg as a remote 
procedure call).
The node will then process the package and in turn forward the package to the 
next node, if itself is not the final destination.

@@

\subsection{\Acf*{SPORES}}

\dots

To create a probabilistic onion route \(H_\rdv\) from a rendez-vous point to 
his own device swarm --- all the hops on the route are chosen by Bob uniformly 
at random.
Bob gives \(H_\rdv\) to Alice using an out-of-band channel, \eg using his phone.
Alice uses \(\SPOR[\Send]\) at some later time to send the message to Bob using 
any of her devices.
\(\SPOR[\Send]\) extends the route \(H_\rdv\) with some hops of Alice's 
choosing (uniformly randomly chosen), then starts to forward the message (using 
\(\SPOR[\Fwd]\)) through the hops on the route to Bob.
This process is illustrated in \cref{fig:file-exchange}.

\begin{figure}
  \includegraphics[width=\linewidth]{figures/file_exchange_v2.pdf}
  \caption{\label{fig:file-exchange}%
    A schematic of Alice and Bob sending a message using \(\SPORES\).
    \ding{1} illustrates the layer of the headers that Alice and Bob create.
    In \ding{2}, Alice and Bob exchange the headers out-of-band.
    In \ding{3}, Alice and Bob use two \ac{SPOR} routes, one for messages and 
    one for acknowledgements.
  }
\end{figure}

### 2018-07-10 paper/sphinxes.tex
Starts adding Sphinxes algorithms
Minor updates to Sphinxes
WIP editing of algorithms

We will now extend Sphinx: instead of providing only \(d_{i+1}\) in 
\(\beta_i\), we will have a set \(\{d_{i+1}^{(0)}, \dotsc, d_{i+1}^{(m)}\}\) of 
\(m\) alternative next nodes.
This means that all \(m\) nodes must be able to compute the same shared secret 
\(s_{i+1}\).
We do this by adding one layer of indirection.

@@

\subsubsection{Sphinxes algorithms}

>>>>

We will now extend Sphinx to do \ac{POR}: instead of providing only \(d_{i+1}\) 
in \(\beta_i\), we will have a set \(\{d_{i+1}^{(0)}, \dotsc, d_{i+1}^{(m)}\}\) 
of \(m\) alternative next nodes.
This means that all \(m\) nodes must be able to compute the same shared secret 
\(s_{i+1}\).
We do this by adding one layer of indirection.

@@

\subsubsection{Sphinxes algorithms and \acf*{POR}}

\NewScheme{\Sphinxes}{Sphxs}
\NewAlgorithm{\CreateHeader}{\Sphinxes[CreateHeader]}
\NewAlgorithm{\CreateFwd}{\Sphinxes[CreateFwd]}
\NewAlgorithm{\CreateRe}{\Sphinxes[CreateReply]}
\NewAlgorithm{\WrapRe}{\Sphinxes[WrapReply]}
\NewAlgorithm{\Process}{\Sphinxes[Process]}

Sphinxes provides the following algorithms:
\begin{itemize}
  \item \(\CreateHeader\) creates a header, this is a modification of that of 
    Sphinx~\cite[\S 3.2]{Sphinx};
  \item \(\CreateFwd\) creates a forward message, this is identical to that of 
    Sphinx~\cite[\S 3.3]{Sphinx};
  \item \(\CreateRe\) creates a single-use reply block, it is the same as in 
    Sphinx~\cite[\S 3.4]{Sphinx} except that it also outputs the necessary keys 
    to wrap it;
  \item \(\WrapRe\) is used to wrap a given single-use reply block; finally
  \item \(\Process\) is the algorithm for processing incoming messages, the 
    processing is identical to Sphinx~\cite[\S 3.6, \S 3.7]{Sphinx} but uses a 
    different interface.
\end{itemize}

\NewAlgorithm{\ExtendRoute}{ExtendRoute}
\NewAlgorithm{\CreateOnionLayer}{CreateOnionLayer}

\begin{figure}
  \framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}[1]
    \Require{%
      $H$ is a header of the form \(D\concat H'\) or \(D\concat \top\), where 
      \(D\) is a set of device addresses.
      $\pk_D$ is the public key of device set $D$.
      $L$ is the length of the route,
      $\theta$ is the threshold of probability of failure.%
    }
    \Function{\ExtendRoute}{$H, L, \theta$}
      \If{$L\leq 0$}
        \State \Return $H$
      \EndIf
      \State $D\gets \CreateOnionLayer[\theta]$
      \State $H\gets D\concat \DeBEenc[\mpk, D, H]$
      \State \Return $\ExtendRoute[H, L-1, \theta]$
    \EndFunction

    \Function{\CreateOnionLayer}{$\theta$}
      \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
      \State $D\gets \{(d, \pk_d, p_d)\}$
      \While{$\prod_{d\in D} p_d > \theta$}
        \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
        \State $D\gets D\cup \{(d, \pk_d, p_d)\}$
      \EndWhile
      \State \Return $D$
    \EndFunction
  \end{algorithmic}
  \end{minipage}}
  \caption{\label{ExtendRoute}%
    The \(\ExtendRoute\) algorithm extends a route \(H\) with \(L\) hops and 
    failure threshold of \(\theta\) for each hop in the route.
    Thus the probability of failure for the extension is \(1 - (1 - \theta)^L\).
    The function \(\GetRandomPeer\) is any random peer-sampling algorithm.
  }
\end{figure}
